How Important are Usage Examples in REST API Documentation?

### 2017-02-27 controlled_study.tex
probably all refs added

\subsubsection{API Learning Obstacles}
  Researchers have published several papers on the topic of API learning obstacles. Robillard et al. used a mixed approach of surveys and in-person interviews with professional software engineers to understand the API learning obstacles \cite{Robillard_what_makes} \cite{Robillard_a_field_study}. They found that API documentation was related to one of the most severe obstacles for API learnabilty and recommended considering five factors for API documentation as follows: documentation of intent, code examples, matching APIs with scenarios, penetrability of the API, and format and presentation. Gias et al. surveyed 323 professional software engineers to understand the factors that fail a API documentation \cite{g_uddin}. They identified ambiguity, incompleteness, and incorrectness as the three severest problems that lead API documentations to fail to answer the information needs of developers. Duala-Ekoko et al. performed a study with twenty programmers to understand the types of questions that developers have while using an unfamiliar API \cite{Duala-Ekoko:2012:AAQ:2337223.2337255}. They categorized the API related information needs into twenty generic questions that can be used to analyze the quality of API documentation.

@@

\subsubsection{Measuring API Usability}
Several papers have been published on the topic of measuring API usability. Rama et al. presented a set of formulas for computing a measure of API usability based on the API's structural components such as classes, methods, parameters, return values, thread-safety, etc \cite{rama}. Scheller et al. presented a framework for automatically measuring the complexity of an API \cite{scheller2015automated}. They identified a list of measurable API properties and provided formulas to compute complexities related to the interfaces, implementation and setup of an API. Grill et al. proposed an HCI based approach that can be used by API developers to understand and improve on the problem areas related to an API \cite{Grill2012}. They suggested using a combination of expert opinion and developer workshops on APIs to identify and collect feedback about API and its documentation related problems. In our work, instead of measuring overall API usability, we have focused specifically on the relationship of REST API usability with respect to usage examples.

>>>>

\subsubsection{API Learning Obstacles}
  Researchers have published several papers on the topic of API learning obstacles. Robillard et al. used a mixed approach of surveys and in-person interviews with professional software engineers to understand the API learning obstacles \cite{Robillard_what_makes} \cite{Robillard_a_field_study}. They found that API documentation was related to one of the most severe obstacles for API learnabilty and recommended considering five factors for API documentation as follows: documentation of intent, code examples, matching APIs with scenarios, penetrability of the API, and format and presentation. Gias et al. surveyed 323 professional software engineers to understand the factors that fail a API documentation \cite{g_uddin}. They identified ambiguity, incompleteness, and incorrectness as the three severest problems that lead API documentations to fail to answer the information needs of developers. Duala-Ekoko et al. performed a study with twenty programmers to understand the types of questions that developers have while using an unfamiliar API \cite{Duala-Ekoko:2012:AAQ:2337223.2337255}. They categorized the API related information needs into twenty generic questions that can be used to analyze the quality of API documentation. Myers et al. performed a study of enterprise SOA API usability and found that the study participants had limited success finding the relevant API elements to perform an API task \cite{Myers_study}. Among other factors, they recommended providing code examples in the API documentation to help API client developers with sample solutions to different patterns of API tasks.

@@

\subsubsection{Measuring API Usability}
Several papers have been published on the topic of measuring API usability. Rama et al. presented a set of formulas for computing a measure of API usability based on the API's structural components such as classes, methods, parameters, return values, thread-safety, etc \cite{rama}. Scheller et al. presented a framework for automatically measuring the complexity of an API \cite{scheller2015automated}. They identified a list of measurable API properties and provided formulas to compute complexities related to the interfaces, implementation and setup of an API. Grill et al. proposed an HCI based approach that can be used by API developers to understand and improve on the problem areas related to an API \cite{Grill2012}. They suggested using a combination of expert opinion and developer workshops on APIs to identify and collect feedback about API and its documentation related problems. To improve API usability, Farooq et al. proposed using peer reviews of API code in addition to API usability studies to uncover API related bugs and incorporate feedback regarding the API elements \cite{Farooq:2010:AUP:1753326.1753677}. In our work, instead of measuring overall API usability, we have focused specifically on the relationship of REST API usability with respect to usage examples.
